Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
update references to demo figures

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row (1
  in Figure~\ref{fig:creating}).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (3 \& 4 in Figure~\ref{fig:creating}).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (5 in Figure~\ref{fig:creating}).
\end{itemize}

@@

Next, she performs a similar process to fill the next column with the
weather descriptions. After filling both columns, she also tries
hovering over previously scraped data, and the toolbar at the top of the
page indicates which column corresponds to the previously scraped data.
Finally, she ends the adapter creation process (7 in
Figure~\ref{fig:creating}) and is able to immediately sort the forecast
by the weather description column, because Wildcard provides a
\textbf{unified environment} that combines both scraping and
customizing.

@@

Jen uses Wildcard on timeanddate.com as can be seen from 1 in
Figure~\ref{fig:extending}. In addition to sorting the list of holidays
in a year by the day of the week, she also wants to sort them by
category so she can view all the federal holidays together. Previously,
she would have needed to find a programmer to help her edit the adapter
code to incorporate this additional data, but using our system's support
for \textbf{editing by demonstration}, Jen can extend the adapter
herself.

@@

While viewing the website, she clicks the ``Edit Adapter'' button (2 in
Figure~\ref{fig:extending}) above the Wildcard table to initiate the
adapter editing process. As she hovers over the currently scraped
values, the columns they belong to are highlighted. Finally, she clicks
on ``Federal Holiday'' (3 in Figure~\ref{fig:extending}) to add the new
column of data to the table (4 in Figure~\ref{fig:extending}) and saves
the changes (5 in Figure~\ref{fig:extending}). Jen then proceeds to sort
the list by the type of holiday without the intervention of a
programmer.

@@

Jen next visits Google Scholar to look up references for her thesis
project. Unfortunately, the customization she had applied to sort
publications by their title (which is not natively supported by Google
Scholar) is no longer working. In fact, the column in the Wildcard table
that contained all the publication titles is empty (1 in
Figure~\ref{fig:repairing}), because the website's internals changed and
broke the adapter's scraping logic. Jen can repair this on her own,
again taking advantage of \textbf{editing by demonstration}.

Jen initiates the editing process (2 in Figure~\ref{fig:repairing}), and
initially hovers over the desired value to demonstrate the column she
wants to scrape. However, the \textbf{live programming} interface
indicates to her that the values would be populated into column D;
instead, she wants the values to be inserted into column A where they
previously appeared. So, Jen clicks on the symbol for column A (3 in
Figure~\ref{fig:repairing}) to indicate that she wants to scrape the
values into that column and demonstrates the first publication title (4
in Figure~\ref{fig:repairing}). The missing values are now back in the
table (5 in Figure~\ref{fig:repairing}). She then proceeds to save her
changes (6 in fig:repairing) and re-apply her customization to the
website by sorting the publications by their title without the
intervention of a programmer.

>>>>

The workflow steps are shown in Figure~\ref{fig:creating}:

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row
  (Part 1).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (Part 3 and 4).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (Part 5).
\end{itemize}

@@

Next, she performs a similar process to fill the next column with the
weather descriptions. After filling both columns, she also tries
hovering over previously scraped data, and the toolbar at the top of the
page indicates which column corresponds to the previously scraped data.
Finally, she ends the adapter creation process (Part 7) and is able to
immediately sort the forecast by the weather description column, because
Wildcard provides a \textbf{unified environment} that combines both
scraping and customizing.

@@

Jen uses Wildcard on timeanddate.com. In addition to sorting the list of
holidays in a year by the day of the week, she also wants to sort them
by category so she can view all the federal holidays together.
Previously, she would have needed to find a programmer to help her edit
the adapter code to incorporate this additional data, but using our
system's support for \textbf{editing by demonstration}, Jen can extend
the adapter herself.

@@

The workflow is shown in Figure~\ref{fig:extending}. While viewing the
website, she clicks the ``Edit Adapter'' button (Part 2) above the
Wildcard table to initiate the adapter editing process. As she hovers
over the currently scraped values, the columns they belong to are
highlighted. Finally, she clicks on ``Federal Holiday'' (Part 3) to add
the new column of data to the table (Part 4) and saves the changes (Part
5). Jen then proceeds to sort the list by the type of holiday without
the intervention of a programmer.

@@

Jen next visits Google Scholar to look up references for her thesis
project. Unfortunately, the customization she had applied to sort
publications by their title (which is not natively supported by Google
Scholar) is no longer working. In fact, the column in the Wildcard table
that contained all the publication titles is empty, because the
website's internals changed and broke the adapter's scraping logic. Jen
can repair this on her own, again taking advantage of \textbf{editing by
demonstration}.

The workflow is shown in Figure~\ref{fig:repairing}. Jen initiates the
editing process (Part 2), and initially hovers over the desired value to
demonstrate the column she wants to scrape. However, the \textbf{live
programming} interface indicates to her that the values would be
populated into column D; instead, she wants the values to be inserted
into column A where they previously appeared. So, Jen clicks on the
symbol for column A (Part 3) to indicate that she wants to scrape the
values into that column and demonstrates the first publication title
(Part 4). The missing values are now back in the table (Part 5). She
then proceeds to save her changes (Part 6) and re-apply her
customization to the website by sorting the publications by their title
without the intervention of a programmer.
